% Make sure to keep the text within the brackets and the output should turn out correct
\acknowledge{%
I want to first and foremost thank Jacobo Konigsberg for giving me the opportunity to work and learn under his guidance. Because of this, I was able to contribute to a long-awaited and historic result at the cutting edge of the field. I could not have asked for a better advisor, and I will cherish his invaluable support and instruction. I also want to thank Ivan Furic and Darin Acosta for providing undergraduate research opportunities that inspired my continued work on the CMS experiment and awakened my interest in machine learning. As our research is made possible by the University of Florida and the U.S. Department of Energy, I thank them for their support.

I also want to recognize and thank the CMS collaboration and those involved in LHC operations, whose tireless work continues to produce datasets of epic size that are a joy to explore. During my time at CERN, the Cookman's welcomed me into their home and I am grateful for their hospitality. I also thank the colleagues and office mates who enriched my time at Fermilab, specifically Souvik Das, Jia Fu Low, and Caterina Vernieri. Such a challenging analysis wouldn't have been a success without the shared vision and expertise of the \VHbb\ analysis team, so I thank and congratulate my closest colleagues on the job well done. Special thanks go to Michele de Gruttola and Christopher Palmer for their mentorship.

I thank my family for their endless love and encouragement and for giving me the freedom to choose how I might make the world a better place. I also thank my wife, Gwynndolyn, who has shown amazing patience and understanding while I travelled around the world chasing particles. I am forever grateful for her love and sacrifice which has allowed me to pursue my research. And finally, I thank God, who after creating the whirling cosmos saw fit to fashion humanity with the means to not only perceive its beauty but also fathom its design.
}
